The Leaky Semicolon

### 2021-10-18 paper/tool.tex
Revert "Add some text about complexity to tool.tex"
This reverts commit bd93a204e11ab22df60e343434c751dba2c096a1.

The compositional nature of the semantics makes tool building practical, but it is not enough to make it scalable for large tests.
The execution times give a good indication the poor scaling of the tool with program size: for larger test cases, the tool takes exponentially longer to compute, and for the largest tests the memory footprint is too large for even a well-equipped computer.
The definitions of $\sSEMI{\aPSS_1}{\aPSS_2}$ and $\sIF{\aForm}\sTHEN\aPSS_1\sELSE\aPSS_2\sFI$ -- in combination with the rules for reads and writes -- yields a complexity class of $\mathcal{O}((|\Val| + 1)^{n})$ where $n$ is the length of the longest chain of sequential compositions in the program.
Some further optimisations may be possible within the tool to improve the situation, such as killing 'dead-end' pomsets at each sequence operator, or by doing a directed search for particular execution outcomes.
Unsurprisingly the execution time is dominated by the calculation of the denotation, with the additional axiomatic filtering step of \PwTc{} being within margin of error difference of just calculating the \PwT{} semantics. 
% \PwTer{} will be made open source upon publication.
\PwTer{} is available online at \url{https://github.com/graymalkin/pomsets-with-predicate-transformers}.

>>>>

The execution times give a good indication the poor scaling of the tool with program size: for larger test cases, the tool takes exponentially longer to compute, and in some cases simply fails.
The compositional nature of the semantics makes tool building practical, but it is not enough to make it scalable for large tests.
Unsurprisingly the execution time is dominated by the calculation of the denotation, with the additional axiomatic filtering step of \PwTc{} being within margin of error difference of just calculating the \PwT{} semantics. 
% \PwTer{} will be made open source upon publication.
\PwTer{} is available online at \url{https://github.com/graymalkin/pomsets-with-predicate-transformers}.
